A GPU Sonar Simulator for Automatic Target Recognition

### 2014-04-27 UAM2014/Article/article.tex
la2pdf commit - 2014:04:28	00:14:37	(Mon28.Apr)

@@

\begin{figure}[t]\centering%
\begin{subfigure}[b]{.5\linewidth-0.5cm}
\graphicsAI[drawing,width=\linewidth]{gfx/data_cylinder_submerged.svg}%
\caption{SAS image of a cylinder with 2.6\;m length and 0.53\;m radius.}\label{cutmean}%
\end{subfigure}\hspace{1cm}%
\begin{subfigure}[b]{.5\linewidth-0.5cm}
\graphicsAI[drawing,width=\linewidth]{gfx/data_cylinder_submerged_bw.svg}%
\caption{SAS image of a cylinder with 2.6\;m length and 0.53\;m radius.}\label{cutmean}%
\end{subfigure} 
\end{figure}

>>>>

% Tune floats
\renewcommand{\topfraction}{0.9}  % max fraction of floats at top
\renewcommand{\bottomfraction}{0.8} % max fraction of floats at bottom
%   Parameters for TEXT pages (not float pages):
\setcounter{topnumber}{2}
\setcounter{bottomnumber}{2}
\setcounter{totalnumber}{4}     % 2 may work better
\setcounter{dbltopnumber}{2}    % for 2-column pages
\renewcommand{\dbltopfraction}{0.9} % fit big float above 2-col. text
\renewcommand{\textfraction}{0.07}  % allow minimal text w. figs
%   Parameters for FLOAT pages (not text pages):
\renewcommand{\floatpagefraction}{0.85}  % require fuller float pages
% N.B.: floatpagefraction MUST be less than topfraction !!
\renewcommand{\dblfloatpagefraction}{0.85} % require fuller float pages

@@

\newlength\imgspacing\setlength\imgspacing{.5cm}

\begin{figure}[tp]\centering%
\begin{subfigure}[b]{.5\linewidth-\imgspacing/2}
\graphicsAI[drawing,width=\linewidth]{gfx/data_cylinder_submerged.svg}%
\caption{SAS image of a cylinder with 2.6\;m length and 0.53\;m radius.}\label{data_sylinder}%
\end{subfigure}\hspace{\imgspacing}%
\begin{subfigure}[b]{.5\linewidth-\imgspacing/2}
\graphicsAI[drawing,width=\linewidth]{gfx/data_cylinder_submerged_bw.svg}%
\caption{SAS image of a cylinder with 2.6\;m length and 0.53\;m radius.}\label{data_cylinder_bw}%
\end{subfigure} 
\end{figure}

\begin{figure}[tp]\centering%
\begin{subfigure}[b]{.5\linewidth-\imgspacing/2}
\graphicsAI[drawing,width=\linewidth]{gfx/sim_cylinder_submerged.svg}%
\caption{Simulated cylinder.}\label{sim_cylinder}%
\end{subfigure}\hspace{\imgspacing}%
\begin{subfigure}[b]{.5\linewidth-\imgspacing/2}
\graphicsAI[drawing,width=\linewidth]{gfx/sim_cylinder_submerged_bw.svg}%
\caption{Simulated cylinder.}\label{sim_cylinder_bw}%
\end{subfigure} 
\end{figure}

\begin{figure}[tp]\centering%
\begin{subfigure}[b]{.5\linewidth-\imgspacing/2}
\graphicsAI[drawing,width=\linewidth]{gfx/overlay_cylinder_submerged.svg}%
\caption{Overlay.}\label{overlay_cylinder}%
\end{subfigure}\hspace{\imgspacing}%
\begin{subfigure}[b]{.5\linewidth-\imgspacing/2}
\graphicsAI[width=\linewidth]{gfx/overlay_cylinder_submerged_adaptive.svg}%
\caption{Overlay (adaptive).}\label{overlay_cylinder_adaptive}%
\end{subfigure} 
\end{figure}

\begin{figure}[tp]\centering%
\graphicsAI[drawing,width=\linewidth]{gfx/overlay_colors.svg}%
\caption{Overlay.}\label{overlay_cylinder}%
\end{figure}
